---
title: "Homwork 1"
author: Shuhong Xiang
output: github_document
---

This is my solution to homework 1

```{r}
library(tidyverse)
```


##Problem 1

Create a data frame with the specified elements. 

```{r create_df}
prob1_df =
  tibble(
   samp = rnorm(10), 
   samp_gt_0 = samp > 0,
   char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"), 
   factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "high", "high", "high", "high"))
  )
```

Take the mean of variables in the data frame

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```
I can take the mean of numbers and logical but not character or factor. 

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
```

##Problem2

```{r}
data("penguins", package = "palmerpenguins")
```


A short description of the penguins data set:

The data set includes species, island, bill_length_mm, bill_depth_mm, body_mass_g, sex and year of the penguins. The species, island, year and sex are characteristic factors. The bill_length_MM and bill_depth_MM are numerical factors.The data set has 344 rows and 8 columns corresponding to the eight variables. The mean of the flipper length is NA due the missing data set.

The size of the data set:

```{r}
nrow(penguins)
ncol(penguins)
```

The the mean flipper length:

```{r}
mean(pull(penguins, flipper_length_mm))
```

Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable :

```{r}
library(ggplot2)
```
Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable:

```{r}
scatterplot = ggplot(penguins, aes(x = bill_length_mm, y = bill_length_mm), color = species)

ggsave("catterplot of flipper lengthin mm.png")
```

